sensiAnPaper1All

### 2016-01-26 effectOfIndividualInputs.Rmd
adding option for extended experiment & start of PRCCs

The plots show a set of points at 1000 generations. The model is run for 500 generations, any runs which have not reached the resistance threshold by this time are given a value of 1000. This has little effect on questions of whether mixtures or sequential use is better, but does effect the plots presented here.

@@

  ## to load previously saved runs
  load(file=paste0(outFolder,'listOutMix_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_1000.rda'))
```

@@

@@

@@

  #exposure has the most noticeable effect
  ggplot(ggInsOuts, aes(x=exposure, y=time_to_resistance0.25, color=strategy)) + 
    geom_point() + 
    facet_wrap( ~ strategy) + 
    #geom_smooth(aes(x=exposure, y=gen_cP0.5, color=NULL))
    geom_smooth(colour='red', linetype='dashed',size=0.5)

@@

  #doing; for all inputs
  names_inputs <- names(ggInsOuts)[1:10]

@@

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             geom_point() + 
             facet_wrap( ~ strategy) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             geom_smooth(colour='red', linetype='dashed',size=0.5) )
  }

@@

>>>>

Runs where resistance thresholds have not been reached have been removed.

Previous plots showed a set of points at 1000 generations. The model is run for 500 generations, any runs which have not reached the resistance threshold by this time are given a value of 1000. This has little effect on questions of whether mixtures or sequential use is better.

@@

  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  ## trying with the extended experiment _ex100
  experiment <- 'extended'
  load(file=paste0(outFolder,'listOutMix_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex1000.rda'))

@@

  #add these for extended analysis
  if (experiment=='extended')
    treePredictors <- c(treePredictors,'maleExposureProp','correctMixDeployProp')

@@

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which(ggInsOuts$gen_cP0.5 == 999 | ggInsOuts$gen_cP0.5 > 500 |
                            ggInsOuts$gen_cP0.25 == 999 | ggInsOuts$gen_cP0.25 > 500 |
                            ggInsOuts$gen_cP0.1 == 999 | ggInsOuts$gen_cP0.1 > 500 )

  #subset by runs not making threshold
  ggInsOuts <- ggInsOuts[-didntReachThresh,]

@@

  #exposure has the most noticeable effect
  ggplot(ggInsOuts, aes(x=exposure, y=time_to_resistance0.25, color=strategy)) + 
    geom_point(shape=3) + 
    facet_wrap( ~ strategy) + 
    #geom_smooth(aes(x=exposure, y=gen_cP0.5, color=NULL))
    geom_smooth(colour='red', linetype='dashed',size=0.5)

@@

  #doing; for all inputs
  if (experiment=='extended') {
    num_inputs <- 13
    } else {
    num_inputs <- 11  
    }

  names_inputs <- names(ggInsOuts)[1:num_inputs]

@@

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             geom_point(shape=3) + 
             facet_wrap( ~ strategy) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             geom_smooth(colour='red', linetype='dashed',size=0.5) +
             labs(title = i))
  }

@@

## Looking more closely at effect of the ratio between the level of resistance to the first insecticide divided by that of the second one. Restricting the x axis to lower values.
```{r, eval=TRUE, echo=FALSE}

  i <- 'resist_start_1_div_2'
  color <- "start_freq_allele2"

  print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
           geom_point(shape=3) + 
           facet_wrap( ~ strategy) + 
           #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
           geom_smooth(colour='red', linetype='dashed',size=0.5) +
           labs(title = i) +
           xlim(0,100)
         )

#trying a PRCC analysis using the package sensitivity
```{r, eval=TRUE, echo=FALSE}

  library(sensitivity)

# pcc(X, y, rank = FALSE, nboot = 0, conf = 0.95)
# 
# ## S3 method for class 'pcc'
# plot(x, ylim = c(-1,1), ...)
# 
# Arguments
# X a data frame containing model input variables
# y a vector containing the responses 
# rank logical. If TRUE, the analysis is done on the ranks.
# nboot the number of bootstrap replicates.
# conf the confidence level of the bootstrap confidence intervals.

  #first attempt
  by_strategy <- ggInsOuts[ggInsOuts$strategy=='insecticide 1',]

  x <- by_strategy[,1:num_inputs]
  y <- by_strategy['time_to_resistance0.25']

  pcc_res <- pcc(x, y, rank=TRUE)

  #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
  #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
  #plot(pcc_res)

  #results are here I can probably rbind them together into a df that I can ggplot
  #pcc_res$PRCC

  to_plot <- pcc_res$PRCC
  to_plot$test <- c(1:nrow(to_plot))
  to_plot$names <- rownames(to_plot)

  ggplot( to_plot, aes_string(x='names',y='original') ) + 
           geom_point(shape=3) +
           theme(axis.text.x = element_text(angle = 45))
